---
title: "TTT Phase 2 Primary Analyses: Youth BHS-4"
author: "Damien Lekkas"
date: "2026-06-19"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

0. LOAD REQUIRED PACKAGES
```{r }
library(dplyr)
library(tidyr)
library(nlme)
library(emmeans)
library(ggplot2)
```


1. GET ITT SAMPLE TO ANALYZE (n = 215)
```{r }

cohort_indicators <- readRDS("/users/Damien/Desktop/TTT_Phase2_Analyses/Cleaned_Data/2026-05-11_v1.0_Phase 2 Cohort Indicators for Flow and Analysis.rds")
itt_sample_ids <- cohort_indicators$lsmh_id[which(cohort_indicators$analyze_itt_sample == TRUE)]

```


2. READ IN YOUTH DATA AND SUBSET BY ITT SAMPLE ID
```{r }

youth_data_IN <- readRDS("/users/Damien/Desktop/TTT_Phase2_Analyses/Cleaned_Data/2026-05-11_v1.0_Phase 2 Youth Qualtrics Clean Data - All Waves.rds")
youth_itt_data <- youth_data_IN[which(youth_data_IN$lsmh_id %in% itt_sample_ids),]

```


3. READ IN PARENT DATA AND SUBSET BY ITT SAMPLE ID
```{r }

parent_data_IN <- readRDS("/users/Damien/Desktop/TTT_Phase2_Analyses/Cleaned_Data/2026-05-11_v1.0_Phase 2 Parent Qualtrics Clean Data - All Waves.rds")
parent_itt_data <- parent_data_IN[which(parent_data_IN$lsmh_id %in% itt_sample_ids),]

```


4. YOUTH BHS-4 MODEL
```{r }

#Filter Data
youth_bhs_data_wide <- youth_itt_data %>%
  select(matches("lsmh_id"), matches("condition"), contains("bhs_mean"))

#Reshape to Long Format
youth_bhs_data_wide$condition <- factor(youth_bhs_data_wide$condition, levels=c("ST", "BA", "GMI"))
youth_bhs_data_wide <- youth_bhs_data_wide %>% rename(id = lsmh_id)
youth_bhs_data_wide <- youth_bhs_data_wide %>% rename('1' = yb_bhs_mean)
youth_bhs_data_wide <- youth_bhs_data_wide %>% rename('2' = yi_pre_bhs_mean)
youth_bhs_data_wide <- youth_bhs_data_wide %>% rename('3' = yi_post_bhs_mean)
youth_bhs_data_wide <- youth_bhs_data_wide %>% rename('4' = y3m_bhs_mean)
youth_bhs_data_wide <- youth_bhs_data_wide %>% rename('5' = y6m_bhs_mean)
youth_bhs_data_wide <- youth_bhs_data_wide %>% rename('6' = y12m_bhs_mean)
youth_bhs_data_wide <- youth_bhs_data_wide %>% rename('7' = y18m_bhs_mean)
youth_bhs_data_wide <- youth_bhs_data_wide %>% rename('8' = y24m_bhs_mean)

youth_bhs_data_long <- pivot_longer(data = youth_bhs_data_wide, 
                               cols = c("1", "2", "3", "4", "5", "6", "7", "8"),
                               names_to = "time", 
                               values_to = "bhs",
                               values_drop_na = FALSE)
youth_bhs_data_long$time <- as.integer(youth_bhs_data_long$time)

attach(youth_bhs_data_long)
month <- time
month[time == 1] <- 0
month[time == 2] <- "pre"
month[time == 3] <- "post"
month[time == 4] <- 3
month[time == 5] <- 6
month[time == 6] <- 12
month[time == 7] <- 18
month[time == 8] <- 24

month.f <- factor(month, c(0, "pre", "post", 3, 6, 12, 18, 24)) 


#Define Mean Response Model and Unstructured Residual Covariance Model in Advance
fml <- bhs ~ I(month.f == "pre") + I(month.f == "post") + I(month.f == 3) + I(month.f == 6) + I(month.f == 12) + I(month.f == 18) + I(month.f == 24) + 
  I(month.f == "pre" & condition == "BA") + I(month.f == "post" & condition == "BA") + 
  I(month.f == 3 & condition == "BA") + I(month.f == 6 & condition == "BA") + I(month.f == 12 & condition == "BA") + 
  I(month.f == 18 & condition == "BA") + I(month.f == 24 & condition == "BA") +
  I(month.f == "pre" & condition == "GMI") + I(month.f == "post" & condition == "GMI") + 
  I(month.f == 3 & condition == "GMI") + I(month.f == 6 & condition == "GMI") + I(month.f == 12 & condition == "GMI") + 
  I(month.f == 18 & condition == "GMI") + I(month.f == 24 & condition == "GMI")
  
cor_un <- corSymm(form = ~ time | id)
var_un <- varIdent(form = ~ 1 | month.f)

set.seed(10111952)
bhs_mod_OUT <- gls(fml, corr = cor_un, weights = var_un, na.action = na.omit)

desmatrix_bhs_mod_OUT <- model.matrix(bhs_mod_OUT)
colnames(desmatrix_bhs_mod_OUT)
desmatrix_df_bhs_mod_OUT <- data.frame(desmatrix_bhs_mod_OUT)
summary(bhs_mod_OUT)

```


5. COMPUTE MARGINAL MEANS MANUALLY
```{r }

#Create marginal means matrix including dummy variables that parallel the model
mm_grid <- expand.grid(condition = c("ST", "BA", "GMI"), time = c("1", "2", "3", "4", "5", "6", "7", "8"))

mm_grid$t2 <- ifelse(mm_grid$time == "2", 1, 0)
mm_grid$t3 <- ifelse(mm_grid$time == "3", 1, 0)
mm_grid$t4 <- ifelse(mm_grid$time == "4", 1, 0)
mm_grid$t5 <- ifelse(mm_grid$time == "5", 1, 0)
mm_grid$t6 <- ifelse(mm_grid$time == "6", 1, 0)
mm_grid$t7 <- ifelse(mm_grid$time == "7", 1, 0)
mm_grid$t8 <- ifelse(mm_grid$time == "8", 1, 0)

mm_grid$t2_BA <- ifelse(mm_grid$time == "2" & mm_grid$condition == "BA", 1, 0)
mm_grid$t3_BA <- ifelse(mm_grid$time == "3" & mm_grid$condition == "BA", 1, 0)
mm_grid$t4_BA <- ifelse(mm_grid$time == "4" & mm_grid$condition == "BA", 1, 0)
mm_grid$t5_BA <- ifelse(mm_grid$time == "5" & mm_grid$condition == "BA", 1, 0)
mm_grid$t6_BA <- ifelse(mm_grid$time == "6" & mm_grid$condition == "BA", 1, 0)
mm_grid$t7_BA <- ifelse(mm_grid$time == "7" & mm_grid$condition == "BA", 1, 0)
mm_grid$t8_BA <- ifelse(mm_grid$time == "8" & mm_grid$condition == "BA", 1, 0)

mm_grid$t2_GMI <- ifelse(mm_grid$time == "2" & mm_grid$condition == "GMI", 1, 0)
mm_grid$t3_GMI <- ifelse(mm_grid$time == "3" & mm_grid$condition == "GMI", 1, 0)
mm_grid$t4_GMI <- ifelse(mm_grid$time == "4" & mm_grid$condition == "GMI", 1, 0)
mm_grid$t5_GMI <- ifelse(mm_grid$time == "5" & mm_grid$condition == "GMI", 1, 0)
mm_grid$t6_GMI <- ifelse(mm_grid$time == "6" & mm_grid$condition == "GMI", 1, 0)
mm_grid$t7_GMI <- ifelse(mm_grid$time == "7" & mm_grid$condition == "GMI", 1, 0)
mm_grid$t8_GMI <- ifelse(mm_grid$time == "8" & mm_grid$condition == "GMI", 1, 0)

#Get beta weights and their variance-covariance matrix
beta <- coef(bhs_mod_OUT)
vcov_matrix <- vcov(bhs_mod_OUT)


#Create selection vector X
selvect_X <- model.matrix(~ t2 + t3 + t4 + t5 + t6 + t7 + t8 + t2_BA + t3_BA + t4_BA + t5_BA + t6_BA + t7_BA + t8_BA +
                            t2_GMI + t3_GMI + t4_GMI + t5_GMI + t6_GMI + t7_GMI + t8_GMI, data = mm_grid)


#Compute estimated marginal mean = X * beta
mm_grid$marginal_mean <- as.numeric(selvect_X %*% beta)


#Compute SE for marginal mean = sqrt(diag(X*V*X'))
mm_grid$se <- sqrt(diag(selvect_X %*% vcov_matrix %*% t(selvect_X)))


# Compute 95% CI for marginal mean using large-sample normal approximation
mm_grid$ci_lo <- mm_grid$marginal_mean - 1.96 * mm_grid$se
mm_grid$ci_hi <- mm_grid$marginal_mean + 1.96 * mm_grid$se
mm_grid
```


6. SELECT AND CALCULATE CONFIRMATORY CONTRASTS AND CORRECT FOR MULTIPLE HYPOTHESES

6A. BETWEEN-GROUP CONTRASTS (4)
```{r }
btwn_group_contrast_results_df <- data.frame(contrast = character(),
                                             estimate = numeric(),
                                             ci_lo = numeric(),
                                             ci_hi = numeric(),
                                             pvalue = numeric(),
                                             adj_pval = numeric(),
                                             cohens_d = numeric(),
                                             stringsAsFactors = FALSE)


#1. BA VS ST @ post
BA_post <- selvect_X[mm_grid$condition == "BA" & mm_grid$time == "3", , drop = FALSE]
ST_post <- selvect_X[mm_grid$condition == "ST" & mm_grid$time == "3", , drop = FALSE]

#Create contrast vector
contvect <- BA_post - ST_post

#Compute contrast estimate and SE
BA_ST_post_est <- as.numeric(contvect %*% beta)
BA_ST_post_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
BA_ST_post_ci_lo <- BA_ST_post_est - 1.96 * BA_ST_post_se
BA_ST_post_ci_hi <- BA_ST_post_est + 1.96 * BA_ST_post_se

#Compute p value using Wald statistic
BA_ST_post_z <- BA_ST_post_est / BA_ST_post_se
BA_ST_post_p <- 2 * pnorm(abs(BA_ST_post_z), lower.tail = FALSE)



#2. BA VS ST @ 3 MONTHS
BA_3mo <- selvect_X[mm_grid$condition == "BA" & mm_grid$time == "4", , drop = FALSE]
ST_3mo <- selvect_X[mm_grid$condition == "ST" & mm_grid$time == "4", , drop = FALSE]

#Create contrast vector
contvect <- BA_3mo - ST_3mo

#Compute contrast estimate and SE
BA_ST_3mo_est <- as.numeric(contvect %*% beta)
BA_ST_3mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
BA_ST_3mo_ci_lo <- BA_ST_3mo_est - 1.96 * BA_ST_3mo_se
BA_ST_3mo_ci_hi <- BA_ST_3mo_est + 1.96 * BA_ST_3mo_se

#Compute p value using Wald statistic
BA_ST_3mo_z <- BA_ST_3mo_est / BA_ST_3mo_se
BA_ST_3mo_p <- 2 * pnorm(abs(BA_ST_3mo_z), lower.tail = FALSE)



#3. GMI VS ST @ post
GMI_post <- selvect_X[mm_grid$condition == "GMI" & mm_grid$time == "3", , drop = FALSE]
ST_post <- selvect_X[mm_grid$condition == "ST" & mm_grid$time == "3", , drop = FALSE]

#Create contrast vector
contvect <- GMI_post - ST_post

#Compute contrast estimate and SE
GMI_ST_post_est <- as.numeric(contvect %*% beta)
GMI_ST_post_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
GMI_ST_post_ci_lo <- GMI_ST_post_est - 1.96 * GMI_ST_post_se
GMI_ST_post_ci_hi <- GMI_ST_post_est + 1.96 * GMI_ST_post_se

#Compute p value using Wald statistic
GMI_ST_post_z <- GMI_ST_post_est / GMI_ST_post_se
GMI_ST_post_p <- 2 * pnorm(abs(GMI_ST_post_z), lower.tail = FALSE)



#4. GMI VS ST @ 3 MONTHS
GMI_3mo <- selvect_X[mm_grid$condition == "GMI" & mm_grid$time == "4", , drop = FALSE]
ST_3mo <- selvect_X[mm_grid$condition == "ST" & mm_grid$time == "4", , drop = FALSE]

#Create contrast vector
contvect <- GMI_3mo - ST_3mo

#Compute contrast estimate and SE
GMI_ST_3mo_est <- as.numeric(contvect %*% beta)
GMI_ST_3mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
GMI_ST_3mo_ci_lo <- GMI_ST_3mo_est - 1.96 * GMI_ST_3mo_se
GMI_ST_3mo_ci_hi <- GMI_ST_3mo_est + 1.96 * GMI_ST_3mo_se

#Compute p value using Wald statistic
GMI_ST_3mo_z <- GMI_ST_3mo_est / GMI_ST_3mo_se
GMI_ST_3mo_p <- 2 * pnorm(abs(GMI_ST_3mo_z), lower.tail = FALSE)


#Compute adjusted p-values, pooled sd, and Cohens D and put results together
btwn_group_adj_pvals <- p.adjust(c(BA_ST_post_p, BA_ST_3mo_p, GMI_ST_post_p, GMI_ST_3mo_p), "holm")
btwn_group_pooled_sd <- sd(youth_bhs_data_long$bhs[which(youth_bhs_data_long$time == 1)], na.rm = T)

btwn_group_contrast_results_df <- rbind(btwn_group_contrast_results_df,
                                        data.frame(contrast = "BA vs ST @ post", 
                                                estimate = BA_ST_post_est, 
                                                ci_lo = BA_ST_post_ci_lo, 
                                                ci_hi = BA_ST_post_ci_hi, 
                                                pvalue = BA_ST_post_p,
                                                adj_pval = btwn_group_adj_pvals[1],
                                                cohens_d = BA_ST_post_est/btwn_group_pooled_sd))

btwn_group_contrast_results_df <- rbind(btwn_group_contrast_results_df,
                                        data.frame(contrast = "BA vs ST @ 3mo", 
                                                estimate = BA_ST_3mo_est, 
                                                ci_lo = BA_ST_3mo_ci_lo, 
                                                ci_hi = BA_ST_3mo_ci_hi, 
                                                pvalue = BA_ST_3mo_p,
                                                adj_pval = btwn_group_adj_pvals[2],
                                                cohens_d = BA_ST_3mo_est/btwn_group_pooled_sd))

btwn_group_contrast_results_df <- rbind(btwn_group_contrast_results_df,
                                        data.frame(contrast = "GMI vs ST @ post", 
                                                estimate = GMI_ST_post_est, 
                                                ci_lo = GMI_ST_post_ci_lo, 
                                                ci_hi = GMI_ST_post_ci_hi, 
                                                pvalue = GMI_ST_post_p,
                                                adj_pval = btwn_group_adj_pvals[3],
                                                cohens_d = GMI_ST_post_est/btwn_group_pooled_sd))

btwn_group_contrast_results_df <- rbind(btwn_group_contrast_results_df,
                                        data.frame(contrast = "GMI vs ST @ 3mo", 
                                                estimate = GMI_ST_3mo_est, 
                                                ci_lo = GMI_ST_3mo_ci_lo, 
                                                ci_hi = GMI_ST_3mo_ci_hi, 
                                                pvalue = GMI_ST_3mo_p,
                                                adj_pval = btwn_group_adj_pvals[4],
                                                cohens_d = GMI_ST_3mo_est/btwn_group_pooled_sd))

(btwn_group_contrast_results_df)

#Save output table
btwn_group_contrast_results_df <- btwn_group_contrast_results_df %>% mutate(across(where(is.numeric), round, digits = 3))
btwn_group_contrast_results_table_OUT <- flextable(btwn_group_contrast_results_df) %>%
  theme_booktabs() %>%
  autofit()
save_as_docx(btwn_group_contrast_results_table_OUT, path = "/users/Damien/Desktop/youth_BHS-4_confirmatory_btwn_group_contrasts_table.docx")

```

6B. WITHIN-GROUP CONTRASTS (4)
```{r }
within_group_contrast_results_df <- data.frame(contrast = character(),
                                               estimate = numeric(),
                                               ci_lo = numeric(),
                                               ci_hi = numeric(),
                                               pvalue = numeric(),
                                               adj_pval = numeric(),
                                               cohens_d = numeric(),
                                               stringsAsFactors = FALSE)

#1. BA FROM BASELINE TO POST
BA_base <- selvect_X[mm_grid$condition == "BA" & mm_grid$time == "1", , drop = FALSE]
BA_post <- selvect_X[mm_grid$condition == "BA" & mm_grid$time == "3", , drop = FALSE]

#Create contrast vector
contvect <- BA_post - BA_base

#Compute contrast estimate and SE
BA_base_post_est <- as.numeric(contvect %*% beta)
BA_base_post_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
BA_base_post_ci_lo <- BA_base_post_est - 1.96 * BA_base_post_se
BA_base_post_ci_hi <- BA_base_post_est + 1.96 * BA_base_post_se

#Compute p value using Wald statistic
BA_base_post_z <- BA_base_post_est / BA_base_post_se
BA_base_post_p <- 2 * pnorm(abs(BA_base_post_z), lower.tail = FALSE)



#2. BA FROM BASELINE TO 3 MONTHS
BA_base <- selvect_X[mm_grid$condition == "BA" & mm_grid$time == "1", , drop = FALSE]
BA_3mo <- selvect_X[mm_grid$condition == "BA" & mm_grid$time == "4", , drop = FALSE]

#Create contrast vector
contvect <- BA_3mo - BA_base

#Compute contrast estimate and SE
BA_base_3mo_est <- as.numeric(contvect %*% beta)
BA_base_3mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
BA_base_3mo_ci_lo <- BA_base_3mo_est - 1.96 * BA_base_3mo_se
BA_base_3mo_ci_hi <- BA_base_3mo_est + 1.96 * BA_base_3mo_se

#Compute p value using Wald statistic
BA_base_3mo_z <- BA_base_3mo_est / BA_base_3mo_se
BA_base_3mo_p <- 2 * pnorm(abs(BA_base_3mo_z), lower.tail = FALSE)



#3. GMI FROM BASELINE TO POST
GMI_base <- selvect_X[mm_grid$condition == "GMI" & mm_grid$time == "1", , drop = FALSE]
GMI_post <- selvect_X[mm_grid$condition == "GMI" & mm_grid$time == "3", , drop = FALSE]

#Create contrast vector
contvect <- GMI_post - GMI_base

#Compute contrast estimate and SE
GMI_base_post_est <- as.numeric(contvect %*% beta)
GMI_base_post_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
GMI_base_post_ci_lo <- GMI_base_post_est - 1.96 * GMI_base_post_se
GMI_base_post_ci_hi <- GMI_base_post_est + 1.96 * GMI_base_post_se

#Compute p value using Wald statistic
GMI_base_post_z <- GMI_base_post_est / GMI_base_post_se
GMI_base_post_p <- 2 * pnorm(abs(GMI_base_post_z), lower.tail = FALSE)



#4. GMI FROM BASELINE TO 3 MONTHS
GMI_base <- selvect_X[mm_grid$condition == "GMI" & mm_grid$time == "1", , drop = FALSE]
GMI_3mo <- selvect_X[mm_grid$condition == "GMI" & mm_grid$time == "4", , drop = FALSE]

#Create contrast vector
contvect <- GMI_3mo - GMI_base

#Compute contrast estimate and SE
GMI_base_3mo_est <- as.numeric(contvect %*% beta)
GMI_base_3mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
GMI_base_3mo_ci_lo <- GMI_base_3mo_est - 1.96 * GMI_base_3mo_se
GMI_base_3mo_ci_hi <- GMI_base_3mo_est + 1.96 * GMI_base_3mo_se

#Compute p value using Wald statistic
GMI_base_3mo_z <- GMI_base_3mo_est / GMI_base_3mo_se
GMI_base_3mo_p <- 2 * pnorm(abs(GMI_base_3mo_z), lower.tail = FALSE)



#Calculate adjusted p-values, condition-specific baseline sds to compute Cohen's D, and put results together
within_group_adj_pvals <- p.adjust(c(BA_base_post_p, BA_base_3mo_p, GMI_base_post_p, GMI_base_3mo_p), "holm")

BA_baseline_sd <- sd(youth_bhs_data_long$bhs[which(youth_bhs_data_long$time == 1 & youth_bhs_data_long$condition == "BA")], na.rm = T)
GMI_baseline_sd <- sd(youth_bhs_data_long$bhs[which(youth_bhs_data_long$time == 1 & youth_bhs_data_long$condition == "GMI")], na.rm = T)

within_group_contrast_results_df <- rbind(within_group_contrast_results_df,
                                        data.frame(contrast = "BA @ base vs BA @ post", 
                                                estimate = BA_base_post_est, 
                                                ci_lo = BA_base_post_ci_lo, 
                                                ci_hi = BA_base_post_ci_hi, 
                                                pvalue = BA_base_post_p,
                                                adj_pval = within_group_adj_pvals[1],
                                                cohens_d = BA_base_post_est/BA_baseline_sd))

within_group_contrast_results_df <- rbind(within_group_contrast_results_df,
                                        data.frame(contrast = "BA @ base vs BA @ 3mo", 
                                                estimate = BA_base_3mo_est, 
                                                ci_lo = BA_base_3mo_ci_lo, 
                                                ci_hi = BA_base_3mo_ci_hi, 
                                                pvalue = BA_base_3mo_p,
                                                adj_pval = within_group_adj_pvals[2],
                                                cohens_d = BA_base_3mo_est/BA_baseline_sd))

within_group_contrast_results_df <- rbind(within_group_contrast_results_df,
                                        data.frame(contrast = "GMI @ base vs GMI @ post", 
                                                estimate = GMI_base_post_est, 
                                                ci_lo = GMI_base_post_ci_lo, 
                                                ci_hi = GMI_base_post_ci_hi, 
                                                pvalue = GMI_base_post_p,
                                                adj_pval = within_group_adj_pvals[3],
                                                cohens_d = GMI_base_post_est/GMI_baseline_sd))

within_group_contrast_results_df <- rbind(within_group_contrast_results_df,
                                        data.frame(contrast = "GMI @ base vs GMI @ 3mo", 
                                                estimate = GMI_base_3mo_est, 
                                                ci_lo = GMI_base_3mo_ci_lo, 
                                                ci_hi = GMI_base_3mo_ci_hi, 
                                                pvalue = GMI_base_3mo_p,
                                                adj_pval = within_group_adj_pvals[4],
                                                cohens_d = GMI_base_3mo_est/GMI_baseline_sd))

(within_group_contrast_results_df)

#Save output table
within_group_contrast_results_df <- within_group_contrast_results_df %>% mutate(across(where(is.numeric), round, digits = 3))
within_group_contrast_results_table_OUT <- flextable(within_group_contrast_results_df) %>%
  theme_booktabs() %>%
  autofit()
save_as_docx(within_group_contrast_results_table_OUT, path = "/users/Damien/Desktop/youth_BHS-4_confirmatory_within_group_contrasts_table.docx")

```


7. SELECT AND CALCULATE EXPLORATORY CONTRASTS AND CORRECT FOR MULTIPLE HYPOTHESES

7A. BETWEEN-GROUP CONTRASTS (12)
```{r }
exp_btwn_group_contrast_results_df <- data.frame(contrast = character(),
                                                 estimate = numeric(),
                                                 ci_lo = numeric(),
                                                 ci_hi = numeric(),
                                                 pvalue = numeric(),
                                                 adj_pval = numeric(),
                                                 cohens_d = numeric(),
                                                 stringsAsFactors = FALSE)

#1. BA VS ST @ 6 MONTHS
BA_6mo <- selvect_X[mm_grid$condition == "BA" & mm_grid$time == "5", , drop = FALSE]
ST_6mo <- selvect_X[mm_grid$condition == "ST" & mm_grid$time == "5", , drop = FALSE]

#Create contrast vector
contvect <- BA_6mo - ST_6mo

#Compute contrast estimate and SE
BA_ST_6mo_est <- as.numeric(contvect %*% beta)
BA_ST_6mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
BA_ST_6mo_ci_lo <- BA_ST_6mo_est - 1.96 * BA_ST_6mo_se
BA_ST_6mo_ci_hi <- BA_ST_6mo_est + 1.96 * BA_ST_6mo_se

#Compute p value using Wald statistic
BA_ST_6mo_z <- BA_ST_6mo_est / BA_ST_6mo_se
BA_ST_6mo_p <- 2 * pnorm(abs(BA_ST_6mo_z), lower.tail = FALSE)



#2. BA VS ST @ 12 MONTHS
BA_12mo <- selvect_X[mm_grid$condition == "BA" & mm_grid$time == "6", , drop = FALSE]
ST_12mo <- selvect_X[mm_grid$condition == "ST" & mm_grid$time == "6", , drop = FALSE]

#Create contrast vector
contvect <- BA_12mo - ST_12mo

#Compute contrast estimate and SE
BA_ST_12mo_est <- as.numeric(contvect %*% beta)
BA_ST_12mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
BA_ST_12mo_ci_lo <- BA_ST_12mo_est - 1.96 * BA_ST_12mo_se
BA_ST_12mo_ci_hi <- BA_ST_12mo_est + 1.96 * BA_ST_12mo_se

#Compute p value using Wald statistic
BA_ST_12mo_z <- BA_ST_12mo_est / BA_ST_12mo_se
BA_ST_12mo_p <- 2 * pnorm(abs(BA_ST_12mo_z), lower.tail = FALSE)



#3. BA VS ST @ 18 MONTHS
BA_18mo <- selvect_X[mm_grid$condition == "BA" & mm_grid$time == "7", , drop = FALSE]
ST_18mo <- selvect_X[mm_grid$condition == "ST" & mm_grid$time == "7", , drop = FALSE]

#Create contrast vector
contvect <- BA_18mo - ST_18mo

#Compute contrast estimate and SE
BA_ST_18mo_est <- as.numeric(contvect %*% beta)
BA_ST_18mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
BA_ST_18mo_ci_lo <- BA_ST_18mo_est - 1.96 * BA_ST_18mo_se
BA_ST_18mo_ci_hi <- BA_ST_18mo_est + 1.96 * BA_ST_18mo_se

#Compute p value using Wald statistic
BA_ST_18mo_z <- BA_ST_18mo_est / BA_ST_18mo_se
BA_ST_18mo_p <- 2 * pnorm(abs(BA_ST_18mo_z), lower.tail = FALSE)



#4. BA VS ST @ 24 MONTHS
BA_24mo <- selvect_X[mm_grid$condition == "BA" & mm_grid$time == "8", , drop = FALSE]
ST_24mo <- selvect_X[mm_grid$condition == "ST" & mm_grid$time == "8", , drop = FALSE]

#Create contrast vector
contvect <- BA_24mo - ST_24mo

#Compute contrast estimate and SE
BA_ST_24mo_est <- as.numeric(contvect %*% beta)
BA_ST_24mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
BA_ST_24mo_ci_lo <- BA_ST_24mo_est - 1.96 * BA_ST_24mo_se
BA_ST_24mo_ci_hi <- BA_ST_24mo_est + 1.96 * BA_ST_24mo_se

#Compute p value using Wald statistic
BA_ST_24mo_z <- BA_ST_24mo_est / BA_ST_24mo_se
BA_ST_24mo_p <- 2 * pnorm(abs(BA_ST_24mo_z), lower.tail = FALSE)



#5. GMI VS ST @ 6 MONTHS
GMI_6mo <- selvect_X[mm_grid$condition == "GMI" & mm_grid$time == "5", , drop = FALSE]
ST_6mo <- selvect_X[mm_grid$condition == "ST" & mm_grid$time == "5", , drop = FALSE]

#Create contrast vector
contvect <- GMI_6mo - ST_6mo

#Compute contrast estimate and SE
GMI_ST_6mo_est <- as.numeric(contvect %*% beta)
GMI_ST_6mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
GMI_ST_6mo_ci_lo <- GMI_ST_6mo_est - 1.96 * GMI_ST_6mo_se
GMI_ST_6mo_ci_hi <- GMI_ST_6mo_est + 1.96 * GMI_ST_6mo_se

#Compute p value using Wald statistic
GMI_ST_6mo_z <- GMI_ST_6mo_est / GMI_ST_6mo_se
GMI_ST_6mo_p <- 2 * pnorm(abs(GMI_ST_6mo_z), lower.tail = FALSE)



#6. GMI VS ST @ 12 MONTHS
GMI_12mo <- selvect_X[mm_grid$condition == "GMI" & mm_grid$time == "6", , drop = FALSE]
ST_12mo <- selvect_X[mm_grid$condition == "ST" & mm_grid$time == "6", , drop = FALSE]

#Create contrast vector
contvect <- GMI_12mo - ST_12mo

#Compute contrast estimate and SE
GMI_ST_12mo_est <- as.numeric(contvect %*% beta)
GMI_ST_12mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
GMI_ST_12mo_ci_lo <- GMI_ST_12mo_est - 1.96 * GMI_ST_12mo_se
GMI_ST_12mo_ci_hi <- GMI_ST_12mo_est + 1.96 * GMI_ST_12mo_se

#Compute p value using Wald statistic
GMI_ST_12mo_z <- GMI_ST_12mo_est / GMI_ST_12mo_se
GMI_ST_12mo_p <- 2 * pnorm(abs(GMI_ST_12mo_z), lower.tail = FALSE)



#7. GMI VS ST @ 18 MONTHS
GMI_18mo <- selvect_X[mm_grid$condition == "GMI" & mm_grid$time == "7", , drop = FALSE]
ST_18mo <- selvect_X[mm_grid$condition == "ST" & mm_grid$time == "7", , drop = FALSE]

#Create contrast vector
contvect <- GMI_18mo - ST_18mo

#Compute contrast estimate and SE
GMI_ST_18mo_est <- as.numeric(contvect %*% beta)
GMI_ST_18mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
GMI_ST_18mo_ci_lo <- GMI_ST_18mo_est - 1.96 * GMI_ST_18mo_se
GMI_ST_18mo_ci_hi <- GMI_ST_18mo_est + 1.96 * GMI_ST_18mo_se

#Compute p value using Wald statistic
GMI_ST_18mo_z <- GMI_ST_18mo_est / GMI_ST_18mo_se
GMI_ST_18mo_p <- 2 * pnorm(abs(GMI_ST_18mo_z), lower.tail = FALSE)



#8. GMI VS ST @ 24 MONTHS
GMI_24mo <- selvect_X[mm_grid$condition == "GMI" & mm_grid$time == "8", , drop = FALSE]
ST_24mo <- selvect_X[mm_grid$condition == "ST" & mm_grid$time == "8", , drop = FALSE]

#Create contrast vector
contvect <- GMI_24mo - ST_24mo

#Compute contrast estimate and SE
GMI_ST_24mo_est <- as.numeric(contvect %*% beta)
GMI_ST_24mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
GMI_ST_24mo_ci_lo <- GMI_ST_24mo_est - 1.96 * GMI_ST_24mo_se
GMI_ST_24mo_ci_hi <- GMI_ST_24mo_est + 1.96 * GMI_ST_24mo_se

#Compute p value using Wald statistic
GMI_ST_24mo_z <- GMI_ST_24mo_est / GMI_ST_24mo_se
GMI_ST_24mo_p <- 2 * pnorm(abs(GMI_ST_24mo_z), lower.tail = FALSE)



#9. BA VS GMI @ 6 MONTHS
BA_6mo <- selvect_X[mm_grid$condition == "BA" & mm_grid$time == "5", , drop = FALSE]
GMI_6mo <- selvect_X[mm_grid$condition == "GMI" & mm_grid$time == "5", , drop = FALSE]

#Create contrast vector
contvect <- BA_6mo - GMI_6mo

#Compute contrast estimate and SE
BA_GMI_6mo_est <- as.numeric(contvect %*% beta)
BA_GMI_6mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
BA_GMI_6mo_ci_lo <- BA_GMI_6mo_est - 1.96 * BA_GMI_6mo_se
BA_GMI_6mo_ci_hi <- BA_GMI_6mo_est + 1.96 * BA_GMI_6mo_se

#Compute p value using Wald statistic
BA_GMI_6mo_z <- BA_GMI_6mo_est / BA_GMI_6mo_se
BA_GMI_6mo_p <- 2 * pnorm(abs(BA_GMI_6mo_z), lower.tail = FALSE)



#10. BA VS GMI @ 12 MONTHS
BA_12mo <- selvect_X[mm_grid$condition == "BA" & mm_grid$time == "6", , drop = FALSE]
GMI_12mo <- selvect_X[mm_grid$condition == "GMI" & mm_grid$time == "6", , drop = FALSE]

#Create contrast vector
contvect <- BA_12mo - GMI_12mo

#Compute contrast estimate and SE
BA_GMI_12mo_est <- as.numeric(contvect %*% beta)
BA_GMI_12mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
BA_GMI_12mo_ci_lo <- BA_GMI_12mo_est - 1.96 * BA_GMI_12mo_se
BA_GMI_12mo_ci_hi <- BA_GMI_12mo_est + 1.96 * BA_GMI_12mo_se

#Compute p value using Wald statistic
BA_GMI_12mo_z <- BA_GMI_12mo_est / BA_GMI_12mo_se
BA_GMI_12mo_p <- 2 * pnorm(abs(BA_GMI_12mo_z), lower.tail = FALSE)



#11. BA VS GMI @ 18 MONTHS
BA_18mo <- selvect_X[mm_grid$condition == "BA" & mm_grid$time == "7", , drop = FALSE]
GMI_18mo <- selvect_X[mm_grid$condition == "GMI" & mm_grid$time == "7", , drop = FALSE]

#Create contrast vector
contvect <- BA_18mo - GMI_18mo

#Compute contrast estimate and SE
BA_GMI_18mo_est <- as.numeric(contvect %*% beta)
BA_GMI_18mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
BA_GMI_18mo_ci_lo <- BA_GMI_18mo_est - 1.96 * BA_GMI_18mo_se
BA_GMI_18mo_ci_hi <- BA_GMI_18mo_est + 1.96 * BA_GMI_18mo_se

#Compute p value using Wald statistic
BA_GMI_18mo_z <- BA_GMI_18mo_est / BA_GMI_18mo_se
BA_GMI_18mo_p <- 2 * pnorm(abs(BA_GMI_18mo_z), lower.tail = FALSE)



#12. BA VS GMI @ 24 MONTHS
BA_24mo <- selvect_X[mm_grid$condition == "BA" & mm_grid$time == "8", , drop = FALSE]
GMI_24mo <- selvect_X[mm_grid$condition == "GMI" & mm_grid$time == "8", , drop = FALSE]

#Create contrast vector
contvect <- BA_24mo - GMI_24mo

#Compute contrast estimate and SE
BA_GMI_24mo_est <- as.numeric(contvect %*% beta)
BA_GMI_24mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
BA_GMI_24mo_ci_lo <- BA_GMI_24mo_est - 1.96 * BA_GMI_24mo_se
BA_GMI_24mo_ci_hi <- BA_GMI_24mo_est + 1.96 * BA_GMI_24mo_se

#Compute p value using Wald statistic
BA_GMI_24mo_z <- BA_GMI_24mo_est / BA_GMI_24mo_se
BA_GMI_24mo_p <- 2 * pnorm(abs(BA_GMI_24mo_z), lower.tail = FALSE)


#Compute adjusted p-values, pooled sd, and Cohens D and put results together
exp_btwn_group_adj_pvals <- p.adjust(c(BA_ST_6mo_p, BA_ST_12mo_p, BA_ST_18mo_p, BA_ST_24mo_p, 
                                       GMI_ST_6mo_p, GMI_ST_12mo_p, GMI_ST_18mo_p, GMI_ST_24mo_p,
                                       BA_GMI_6mo_p, BA_GMI_12mo_p, BA_GMI_18mo_p, BA_GMI_24mo_p), "BH")
exp_btwn_group_pooled_sd <- sd(youth_bhs_data_long$bhs[which(youth_bhs_data_long$time == 1)], na.rm = T)

exp_btwn_group_contrast_results_df <- rbind(exp_btwn_group_contrast_results_df,
                                            data.frame(contrast = "BA vs ST @ 6mo", 
                                                       estimate = BA_ST_6mo_est, 
                                                       ci_lo = BA_ST_6mo_ci_lo, 
                                                       ci_hi = BA_ST_6mo_ci_hi, 
                                                       pvalue = BA_ST_6mo_p,
                                                       adj_pval = exp_btwn_group_adj_pvals[1],
                                                       cohens_d = BA_ST_6mo_est/exp_btwn_group_pooled_sd))

exp_btwn_group_contrast_results_df <- rbind(exp_btwn_group_contrast_results_df,
                                            data.frame(contrast = "BA vs ST @ 12mo", 
                                                       estimate = BA_ST_12mo_est, 
                                                       ci_lo = BA_ST_12mo_ci_lo, 
                                                       ci_hi = BA_ST_12mo_ci_hi, 
                                                       pvalue = BA_ST_12mo_p,
                                                       adj_pval = exp_btwn_group_adj_pvals[2],
                                                       cohens_d = BA_ST_12mo_est/exp_btwn_group_pooled_sd))

exp_btwn_group_contrast_results_df <- rbind(exp_btwn_group_contrast_results_df,
                                            data.frame(contrast = "BA vs ST @ 18mo", 
                                                       estimate = BA_ST_18mo_est, 
                                                       ci_lo = BA_ST_18mo_ci_lo, 
                                                       ci_hi = BA_ST_18mo_ci_hi, 
                                                       pvalue = BA_ST_18mo_p,
                                                       adj_pval = exp_btwn_group_adj_pvals[3],
                                                       cohens_d = BA_ST_18mo_est/exp_btwn_group_pooled_sd))

exp_btwn_group_contrast_results_df <- rbind(exp_btwn_group_contrast_results_df,
                                            data.frame(contrast = "BA vs ST @ 24mo", 
                                                       estimate = BA_ST_24mo_est, 
                                                       ci_lo = BA_ST_24mo_ci_lo, 
                                                       ci_hi = BA_ST_24mo_ci_hi, 
                                                       pvalue = BA_ST_24mo_p,
                                                       adj_pval = exp_btwn_group_adj_pvals[4],
                                                       cohens_d = BA_ST_24mo_est/exp_btwn_group_pooled_sd))

exp_btwn_group_contrast_results_df <- rbind(exp_btwn_group_contrast_results_df,
                                            data.frame(contrast = "GMI vs ST @ 6mo", 
                                                       estimate = GMI_ST_6mo_est, 
                                                       ci_lo = GMI_ST_6mo_ci_lo, 
                                                       ci_hi = GMI_ST_6mo_ci_hi, 
                                                       pvalue = GMI_ST_6mo_p,
                                                       adj_pval = exp_btwn_group_adj_pvals[5],
                                                       cohens_d = GMI_ST_6mo_est/exp_btwn_group_pooled_sd))

exp_btwn_group_contrast_results_df <- rbind(exp_btwn_group_contrast_results_df,
                                            data.frame(contrast = "GMI vs ST @ 12mo", 
                                                       estimate = GMI_ST_12mo_est, 
                                                       ci_lo = GMI_ST_12mo_ci_lo, 
                                                       ci_hi = GMI_ST_12mo_ci_hi, 
                                                       pvalue = GMI_ST_12mo_p,
                                                       adj_pval = exp_btwn_group_adj_pvals[6],
                                                       cohens_d = GMI_ST_12mo_est/exp_btwn_group_pooled_sd))

exp_btwn_group_contrast_results_df <- rbind(exp_btwn_group_contrast_results_df,
                                            data.frame(contrast = "GMI vs ST @ 18mo", 
                                                       estimate = GMI_ST_18mo_est, 
                                                       ci_lo = GMI_ST_18mo_ci_lo, 
                                                       ci_hi = GMI_ST_18mo_ci_hi, 
                                                       pvalue = GMI_ST_18mo_p,
                                                       adj_pval = exp_btwn_group_adj_pvals[7],
                                                       cohens_d = GMI_ST_18mo_est/exp_btwn_group_pooled_sd))

exp_btwn_group_contrast_results_df <- rbind(exp_btwn_group_contrast_results_df,
                                            data.frame(contrast = "GMI vs ST @ 24mo", 
                                                       estimate = GMI_ST_24mo_est, 
                                                       ci_lo = GMI_ST_24mo_ci_lo, 
                                                       ci_hi = GMI_ST_24mo_ci_hi, 
                                                       pvalue = GMI_ST_24mo_p,
                                                       adj_pval = exp_btwn_group_adj_pvals[8],
                                                       cohens_d = GMI_ST_24mo_est/exp_btwn_group_pooled_sd))

exp_btwn_group_contrast_results_df <- rbind(exp_btwn_group_contrast_results_df,
                                            data.frame(contrast = "BA vs GMI @ 6mo", 
                                                       estimate = BA_GMI_6mo_est, 
                                                       ci_lo = BA_GMI_6mo_ci_lo, 
                                                       ci_hi = BA_GMI_6mo_ci_hi, 
                                                       pvalue = BA_GMI_6mo_p,
                                                       adj_pval = exp_btwn_group_adj_pvals[9],
                                                       cohens_d = BA_GMI_6mo_est/exp_btwn_group_pooled_sd))

exp_btwn_group_contrast_results_df <- rbind(exp_btwn_group_contrast_results_df,
                                            data.frame(contrast = "BA vs GMI @ 12mo", 
                                                       estimate = BA_GMI_12mo_est, 
                                                       ci_lo = BA_GMI_12mo_ci_lo, 
                                                       ci_hi = BA_GMI_12mo_ci_hi, 
                                                       pvalue = BA_GMI_12mo_p,
                                                       adj_pval = exp_btwn_group_adj_pvals[10],
                                                       cohens_d = BA_GMI_12mo_est/exp_btwn_group_pooled_sd))

exp_btwn_group_contrast_results_df <- rbind(exp_btwn_group_contrast_results_df,
                                            data.frame(contrast = "BA vs GMI @ 18mo", 
                                                       estimate = BA_GMI_18mo_est, 
                                                       ci_lo = BA_GMI_18mo_ci_lo, 
                                                       ci_hi = BA_GMI_18mo_ci_hi, 
                                                       pvalue = BA_GMI_18mo_p,
                                                       adj_pval = exp_btwn_group_adj_pvals[11],
                                                       cohens_d = BA_GMI_18mo_est/exp_btwn_group_pooled_sd))

exp_btwn_group_contrast_results_df <- rbind(exp_btwn_group_contrast_results_df,
                                            data.frame(contrast = "BA vs GMI @ 24mo", 
                                                       estimate = BA_GMI_24mo_est, 
                                                       ci_lo = BA_GMI_24mo_ci_lo, 
                                                       ci_hi = BA_GMI_24mo_ci_hi, 
                                                       pvalue = BA_GMI_24mo_p,
                                                       adj_pval = exp_btwn_group_adj_pvals[12],
                                                       cohens_d = BA_GMI_24mo_est/exp_btwn_group_pooled_sd))

(exp_btwn_group_contrast_results_df)

#Save output table
exp_btwn_group_contrast_results_df <- exp_btwn_group_contrast_results_df %>% mutate(across(where(is.numeric), round, digits = 3))
exp_btwn_group_contrast_results_table_OUT <- flextable(exp_btwn_group_contrast_results_df) %>%
  theme_booktabs() %>%
  autofit()
save_as_docx(exp_btwn_group_contrast_results_table_OUT, path = "/users/Damien/Desktop/youth_BHS-4_exploratory_btwn_group_contrasts_table.docx")

```


7B. WITHIN-GROUP CONTRASTS (14)
```{r }
exp_within_group_contrast_results_df <- data.frame(contrast = character(),
                                                   estimate = numeric(),
                                                   ci_lo = numeric(),
                                                   ci_hi = numeric(),
                                                   pvalue = numeric(),
                                                   adj_pval = numeric(),
                                                   cohens_d = numeric(),
                                                   stringsAsFactors = FALSE)

#1. BA FROM BASELINE TO 6 MONTHS
BA_base <- selvect_X[mm_grid$condition == "BA" & mm_grid$time == "1", , drop = FALSE]
BA_6mo <- selvect_X[mm_grid$condition == "BA" & mm_grid$time == "5", , drop = FALSE]

#Create contrast vector
contvect <- BA_6mo - BA_base

#Compute contrast estimate and SE
BA_base_6mo_est <- as.numeric(contvect %*% beta)
BA_base_6mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
BA_base_6mo_ci_lo <- BA_base_6mo_est - 1.96 * BA_base_6mo_se
BA_base_6mo_ci_hi <- BA_base_6mo_est + 1.96 * BA_base_6mo_se

#Compute p value using Wald statistic
BA_base_6mo_z <- BA_base_6mo_est / BA_base_6mo_se
BA_base_6mo_p <- 2 * pnorm(abs(BA_base_6mo_z), lower.tail = FALSE)



#2. BA FROM BASELINE TO 12 MONTHS
BA_base <- selvect_X[mm_grid$condition == "BA" & mm_grid$time == "1", , drop = FALSE]
BA_12mo <- selvect_X[mm_grid$condition == "BA" & mm_grid$time == "6", , drop = FALSE]

#Create contrast vector
contvect <- BA_12mo - BA_base

#Compute contrast estimate and SE
BA_base_12mo_est <- as.numeric(contvect %*% beta)
BA_base_12mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
BA_base_12mo_ci_lo <- BA_base_12mo_est - 1.96 * BA_base_12mo_se
BA_base_12mo_ci_hi <- BA_base_12mo_est + 1.96 * BA_base_12mo_se

#Compute p value using Wald statistic
BA_base_12mo_z <- BA_base_12mo_est / BA_base_12mo_se
BA_base_12mo_p <- 2 * pnorm(abs(BA_base_12mo_z), lower.tail = FALSE)



#3. BA FROM BASELINE TO 18 MONTHS
BA_base <- selvect_X[mm_grid$condition == "BA" & mm_grid$time == "1", , drop = FALSE]
BA_18mo <- selvect_X[mm_grid$condition == "BA" & mm_grid$time == "7", , drop = FALSE]

#Create contrast vector
contvect <- BA_18mo - BA_base

#Compute contrast estimate and SE
BA_base_18mo_est <- as.numeric(contvect %*% beta)
BA_base_18mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
BA_base_18mo_ci_lo <- BA_base_18mo_est - 1.96 * BA_base_18mo_se
BA_base_18mo_ci_hi <- BA_base_18mo_est + 1.96 * BA_base_18mo_se

#Compute p value using Wald statistic
BA_base_18mo_z <- BA_base_18mo_est / BA_base_18mo_se
BA_base_18mo_p <- 2 * pnorm(abs(BA_base_18mo_z), lower.tail = FALSE)



#4. BA FROM BASELINE TO 24 MONTHS
BA_base <- selvect_X[mm_grid$condition == "BA" & mm_grid$time == "1", , drop = FALSE]
BA_24mo <- selvect_X[mm_grid$condition == "BA" & mm_grid$time == "8", , drop = FALSE]

#Create contrast vector
contvect <- BA_24mo - BA_base

#Compute contrast estimate and SE
BA_base_24mo_est <- as.numeric(contvect %*% beta)
BA_base_24mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
BA_base_24mo_ci_lo <- BA_base_24mo_est - 1.96 * BA_base_24mo_se
BA_base_24mo_ci_hi <- BA_base_24mo_est + 1.96 * BA_base_24mo_se

#Compute p value using Wald statistic
BA_base_24mo_z <- BA_base_24mo_est / BA_base_24mo_se
BA_base_24mo_p <- 2 * pnorm(abs(BA_base_24mo_z), lower.tail = FALSE)


#5. GMI FROM BASELINE TO 6 MONTHS
GMI_base <- selvect_X[mm_grid$condition == "GMI" & mm_grid$time == "1", , drop = FALSE]
GMI_6mo <- selvect_X[mm_grid$condition == "GMI" & mm_grid$time == "5", , drop = FALSE]

#Create contrast vector
contvect <- GMI_6mo - GMI_base

#Compute contrast estimate and SE
GMI_base_6mo_est <- as.numeric(contvect %*% beta)
GMI_base_6mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
GMI_base_6mo_ci_lo <- GMI_base_6mo_est - 1.96 * GMI_base_6mo_se
GMI_base_6mo_ci_hi <- GMI_base_6mo_est + 1.96 * GMI_base_6mo_se

#Compute p value using Wald statistic
GMI_base_6mo_z <- GMI_base_6mo_est / GMI_base_6mo_se
GMI_base_6mo_p <- 2 * pnorm(abs(GMI_base_6mo_z), lower.tail = FALSE)



#6. GMI FROM BASELINE TO 12 MONTHS
GMI_base <- selvect_X[mm_grid$condition == "GMI" & mm_grid$time == "1", , drop = FALSE]
GMI_12mo <- selvect_X[mm_grid$condition == "GMI" & mm_grid$time == "6", , drop = FALSE]

#Create contrast vector
contvect <- GMI_12mo - GMI_base

#Compute contrast estimate and SE
GMI_base_12mo_est <- as.numeric(contvect %*% beta)
GMI_base_12mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
GMI_base_12mo_ci_lo <- GMI_base_12mo_est - 1.96 * GMI_base_12mo_se
GMI_base_12mo_ci_hi <- GMI_base_12mo_est + 1.96 * GMI_base_12mo_se

#Compute p value using Wald statistic
GMI_base_12mo_z <- GMI_base_12mo_est / GMI_base_12mo_se
GMI_base_12mo_p <- 2 * pnorm(abs(GMI_base_12mo_z), lower.tail = FALSE)



#7. GMI FROM BASELINE TO 18 MONTHS
GMI_base <- selvect_X[mm_grid$condition == "GMI" & mm_grid$time == "1", , drop = FALSE]
GMI_18mo <- selvect_X[mm_grid$condition == "GMI" & mm_grid$time == "7", , drop = FALSE]

#Create contrast vector
contvect <- GMI_18mo - GMI_base

#Compute contrast estimate and SE
GMI_base_18mo_est <- as.numeric(contvect %*% beta)
GMI_base_18mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
GMI_base_18mo_ci_lo <- GMI_base_18mo_est - 1.96 * GMI_base_18mo_se
GMI_base_18mo_ci_hi <- GMI_base_18mo_est + 1.96 * GMI_base_18mo_se

#Compute p value using Wald statistic
GMI_base_18mo_z <- GMI_base_18mo_est / GMI_base_18mo_se
GMI_base_18mo_p <- 2 * pnorm(abs(GMI_base_18mo_z), lower.tail = FALSE)



#8. GMI FROM BASELINE TO 24 MONTHS
GMI_base <- selvect_X[mm_grid$condition == "GMI" & mm_grid$time == "1", , drop = FALSE]
GMI_24mo <- selvect_X[mm_grid$condition == "GMI" & mm_grid$time == "8", , drop = FALSE]

#Create contrast vector
contvect <- GMI_24mo - GMI_base

#Compute contrast estimate and SE
GMI_base_24mo_est <- as.numeric(contvect %*% beta)
GMI_base_24mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
GMI_base_24mo_ci_lo <- GMI_base_24mo_est - 1.96 * GMI_base_24mo_se
GMI_base_24mo_ci_hi <- GMI_base_24mo_est + 1.96 * GMI_base_24mo_se

#Compute p value using Wald statistic
GMI_base_24mo_z <- GMI_base_24mo_est / GMI_base_24mo_se
GMI_base_24mo_p <- 2 * pnorm(abs(GMI_base_24mo_z), lower.tail = FALSE)



#9. ST FROM BASELINE TO POST
ST_base <- selvect_X[mm_grid$condition == "ST" & mm_grid$time == "1", , drop = FALSE]
ST_post <- selvect_X[mm_grid$condition == "ST" & mm_grid$time == "3", , drop = FALSE]

#Create contrast vector
contvect <- ST_post - ST_base

#Compute contrast estimate and SE
ST_base_post_est <- as.numeric(contvect %*% beta)
ST_base_post_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
ST_base_post_ci_lo <- ST_base_post_est - 1.96 * ST_base_post_se
ST_base_post_ci_hi <- ST_base_post_est + 1.96 * ST_base_post_se

#Compute p value using Wald statistic
ST_base_post_z <- ST_base_post_est / ST_base_post_se
ST_base_post_p <- 2 * pnorm(abs(ST_base_post_z), lower.tail = FALSE)



#10. ST FROM BASELINE TO 3 MONTHS
ST_base <- selvect_X[mm_grid$condition == "ST" & mm_grid$time == "1", , drop = FALSE]
ST_3mo <- selvect_X[mm_grid$condition == "ST" & mm_grid$time == "4", , drop = FALSE]

#Create contrast vector
contvect <- ST_3mo - ST_base

#Compute contrast estimate and SE
ST_base_3mo_est <- as.numeric(contvect %*% beta)
ST_base_3mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
ST_base_3mo_ci_lo <- ST_base_3mo_est - 1.96 * ST_base_3mo_se
ST_base_3mo_ci_hi <- ST_base_3mo_est + 1.96 * ST_base_3mo_se

#Compute p value using Wald statistic
ST_base_3mo_z <- ST_base_3mo_est / ST_base_3mo_se
ST_base_3mo_p <- 2 * pnorm(abs(ST_base_3mo_z), lower.tail = FALSE)



#11. ST FROM BASELINE TO 6 MONTHS
ST_base <- selvect_X[mm_grid$condition == "ST" & mm_grid$time == "1", , drop = FALSE]
ST_6mo <- selvect_X[mm_grid$condition == "ST" & mm_grid$time == "5", , drop = FALSE]

#Create contrast vector
contvect <- ST_6mo - ST_base

#Compute contrast estimate and SE
ST_base_6mo_est <- as.numeric(contvect %*% beta)
ST_base_6mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
ST_base_6mo_ci_lo <- ST_base_6mo_est - 1.96 * ST_base_6mo_se
ST_base_6mo_ci_hi <- ST_base_6mo_est + 1.96 * ST_base_6mo_se

#Compute p value using Wald statistic
ST_base_6mo_z <- ST_base_6mo_est / ST_base_6mo_se
ST_base_6mo_p <- 2 * pnorm(abs(ST_base_6mo_z), lower.tail = FALSE)



#12. ST FROM BASELINE TO 12 MONTHS
ST_base <- selvect_X[mm_grid$condition == "ST" & mm_grid$time == "1", , drop = FALSE]
ST_12mo <- selvect_X[mm_grid$condition == "ST" & mm_grid$time == "6", , drop = FALSE]

#Create contrast vector
contvect <- ST_12mo - ST_base

#Compute contrast estimate and SE
ST_base_12mo_est <- as.numeric(contvect %*% beta)
ST_base_12mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
ST_base_12mo_ci_lo <- ST_base_12mo_est - 1.96 * ST_base_12mo_se
ST_base_12mo_ci_hi <- ST_base_12mo_est + 1.96 * ST_base_12mo_se

#Compute p value using Wald statistic
ST_base_12mo_z <- ST_base_12mo_est / ST_base_12mo_se
ST_base_12mo_p <- 2 * pnorm(abs(ST_base_12mo_z), lower.tail = FALSE)



#13. ST FROM BASELINE TO 18 MONTHS
ST_base <- selvect_X[mm_grid$condition == "ST" & mm_grid$time == "1", , drop = FALSE]
ST_18mo <- selvect_X[mm_grid$condition == "ST" & mm_grid$time == "7", , drop = FALSE]

#Create contrast vector
contvect <- ST_18mo - ST_base

#Compute contrast estimate and SE
ST_base_18mo_est <- as.numeric(contvect %*% beta)
ST_base_18mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
ST_base_18mo_ci_lo <- ST_base_18mo_est - 1.96 * ST_base_18mo_se
ST_base_18mo_ci_hi <- ST_base_18mo_est + 1.96 * ST_base_18mo_se

#Compute p value using Wald statistic
ST_base_18mo_z <- ST_base_18mo_est / ST_base_18mo_se
ST_base_18mo_p <- 2 * pnorm(abs(ST_base_18mo_z), lower.tail = FALSE)



#14. ST FROM BASELINE TO 24 MONTHS
ST_base <- selvect_X[mm_grid$condition == "ST" & mm_grid$time == "1", , drop = FALSE]
ST_24mo <- selvect_X[mm_grid$condition == "ST" & mm_grid$time == "8", , drop = FALSE]

#Create contrast vector
contvect <- ST_24mo - ST_base

#Compute contrast estimate and SE
ST_base_24mo_est <- as.numeric(contvect %*% beta)
ST_base_24mo_se  <- sqrt(as.numeric(contvect %*% vcov_matrix %*% t(contvect)))

#Compute 95% CI using large-sample normal approximation
ST_base_24mo_ci_lo <- ST_base_24mo_est - 1.96 * ST_base_24mo_se
ST_base_24mo_ci_hi <- ST_base_24mo_est + 1.96 * ST_base_24mo_se

#Compute p value using Wald statistic
ST_base_24mo_z <- ST_base_24mo_est / ST_base_24mo_se
ST_base_24mo_p <- 2 * pnorm(abs(ST_base_24mo_z), lower.tail = FALSE)


#Calculate adjusted p-values, condition-specific baseline sds to compute Cohen's D, and put results together
exp_within_group_adj_pvals <- p.adjust(c(BA_base_6mo_p, BA_base_12mo_p, BA_base_18mo_p, BA_base_24mo_p, 
                                         GMI_base_6mo_p, GMI_base_12mo_p, GMI_base_18mo_p, GMI_base_24mo_p,
                                         ST_base_post_p, ST_base_3mo_p, ST_base_6mo_p, ST_base_12mo_p, ST_base_18mo_p, ST_base_24mo_p), "BH")

BA_baseline_sd <- sd(youth_bhs_data_long$bhs[which(youth_bhs_data_long$time == 1 & youth_bhs_data_long$condition == "BA")], na.rm = T)
GMI_baseline_sd <- sd(youth_bhs_data_long$bhs[which(youth_bhs_data_long$time == 1 & youth_bhs_data_long$condition == "GMI")], na.rm = T)
ST_baseline_sd <- sd(youth_bhs_data_long$bhs[which(youth_bhs_data_long$time == 1 & youth_bhs_data_long$condition == "ST")], na.rm = T)


exp_within_group_contrast_results_df <- rbind(exp_within_group_contrast_results_df,
                                              data.frame(contrast = "BA @ base vs BA @ 6mo", 
                                                         estimate = BA_base_6mo_est, 
                                                         ci_lo = BA_base_6mo_ci_lo, 
                                                         ci_hi = BA_base_6mo_ci_hi, 
                                                         pvalue = BA_base_6mo_p,
                                                         adj_pval = exp_within_group_adj_pvals[1],
                                                         cohens_d = BA_base_6mo_est/BA_baseline_sd))

exp_within_group_contrast_results_df <- rbind(exp_within_group_contrast_results_df,
                                              data.frame(contrast = "BA @ base vs BA @ 12mo", 
                                                         estimate = BA_base_12mo_est, 
                                                         ci_lo = BA_base_12mo_ci_lo, 
                                                         ci_hi = BA_base_12mo_ci_hi, 
                                                         pvalue = BA_base_12mo_p,
                                                         adj_pval = exp_within_group_adj_pvals[2],
                                                         cohens_d = BA_base_12mo_est/BA_baseline_sd))

exp_within_group_contrast_results_df <- rbind(exp_within_group_contrast_results_df,
                                              data.frame(contrast = "BA @ base vs BA @ 18mo", 
                                                         estimate = BA_base_18mo_est, 
                                                         ci_lo = BA_base_18mo_ci_lo, 
                                                         ci_hi = BA_base_18mo_ci_hi, 
                                                         pvalue = BA_base_18mo_p,
                                                         adj_pval = exp_within_group_adj_pvals[3],
                                                         cohens_d = BA_base_18mo_est/BA_baseline_sd))

exp_within_group_contrast_results_df <- rbind(exp_within_group_contrast_results_df,
                                              data.frame(contrast = "BA @ base vs BA @ 24mo", 
                                                         estimate = BA_base_24mo_est, 
                                                         ci_lo = BA_base_24mo_ci_lo, 
                                                         ci_hi = BA_base_24mo_ci_hi, 
                                                         pvalue = BA_base_24mo_p,
                                                         adj_pval = exp_within_group_adj_pvals[4],
                                                         cohens_d = BA_base_24mo_est/BA_baseline_sd))

exp_within_group_contrast_results_df <- rbind(exp_within_group_contrast_results_df,
                                              data.frame(contrast = "GMI @ base vs GMI @ 6mo", 
                                                         estimate = GMI_base_6mo_est, 
                                                         ci_lo = GMI_base_6mo_ci_lo, 
                                                         ci_hi = GMI_base_6mo_ci_hi, 
                                                         pvalue = GMI_base_6mo_p,
                                                         adj_pval = exp_within_group_adj_pvals[5],
                                                         cohens_d = GMI_base_6mo_est/GMI_baseline_sd))

exp_within_group_contrast_results_df <- rbind(exp_within_group_contrast_results_df,
                                              data.frame(contrast = "GMI @ base vs GMI @ 12mo", 
                                                         estimate = GMI_base_12mo_est, 
                                                         ci_lo = GMI_base_12mo_ci_lo, 
                                                         ci_hi = GMI_base_12mo_ci_hi, 
                                                         pvalue = GMI_base_12mo_p,
                                                         adj_pval = exp_within_group_adj_pvals[6],
                                                         cohens_d = GMI_base_12mo_est/GMI_baseline_sd))

exp_within_group_contrast_results_df <- rbind(exp_within_group_contrast_results_df,
                                              data.frame(contrast = "GMI @ base vs GMI @ 18mo", 
                                                         estimate = GMI_base_18mo_est, 
                                                         ci_lo = GMI_base_18mo_ci_lo, 
                                                         ci_hi = GMI_base_18mo_ci_hi, 
                                                         pvalue = GMI_base_18mo_p,
                                                         adj_pval = exp_within_group_adj_pvals[7],
                                                         cohens_d = GMI_base_18mo_est/GMI_baseline_sd))

exp_within_group_contrast_results_df <- rbind(exp_within_group_contrast_results_df,
                                              data.frame(contrast = "GMI @ base vs GMI @ 24mo", 
                                                         estimate = GMI_base_24mo_est, 
                                                         ci_lo = GMI_base_24mo_ci_lo, 
                                                         ci_hi = GMI_base_24mo_ci_hi, 
                                                         pvalue = GMI_base_24mo_p,
                                                         adj_pval = exp_within_group_adj_pvals[8],
                                                         cohens_d = GMI_base_24mo_est/GMI_baseline_sd))

exp_within_group_contrast_results_df <- rbind(exp_within_group_contrast_results_df,
                                              data.frame(contrast = "ST @ base vs ST @ post", 
                                                         estimate = ST_base_post_est, 
                                                         ci_lo = ST_base_post_ci_lo, 
                                                         ci_hi = ST_base_post_ci_hi, 
                                                         pvalue = ST_base_post_p,
                                                         adj_pval = exp_within_group_adj_pvals[9],
                                                         cohens_d = ST_base_post_est/ST_baseline_sd))

exp_within_group_contrast_results_df <- rbind(exp_within_group_contrast_results_df,
                                              data.frame(contrast = "ST @ base vs ST @ 3mo", 
                                                         estimate = ST_base_3mo_est, 
                                                         ci_lo = ST_base_3mo_ci_lo, 
                                                         ci_hi = ST_base_3mo_ci_hi, 
                                                         pvalue = ST_base_3mo_p,
                                                         adj_pval = exp_within_group_adj_pvals[10],
                                                         cohens_d = ST_base_3mo_est/ST_baseline_sd))

exp_within_group_contrast_results_df <- rbind(exp_within_group_contrast_results_df,
                                              data.frame(contrast = "ST @ base vs ST @ 6mo", 
                                                         estimate = ST_base_6mo_est, 
                                                         ci_lo = ST_base_6mo_ci_lo, 
                                                         ci_hi = ST_base_6mo_ci_hi, 
                                                         pvalue = ST_base_6mo_p,
                                                         adj_pval = exp_within_group_adj_pvals[11],
                                                         cohens_d = ST_base_6mo_est/ST_baseline_sd))

exp_within_group_contrast_results_df <- rbind(exp_within_group_contrast_results_df,
                                              data.frame(contrast = "ST @ base vs ST @ 12mo", 
                                                         estimate = ST_base_12mo_est, 
                                                         ci_lo = ST_base_12mo_ci_lo, 
                                                         ci_hi = ST_base_12mo_ci_hi, 
                                                         pvalue = ST_base_12mo_p,
                                                         adj_pval = exp_within_group_adj_pvals[12],
                                                         cohens_d = ST_base_12mo_est/ST_baseline_sd))

exp_within_group_contrast_results_df <- rbind(exp_within_group_contrast_results_df,
                                              data.frame(contrast = "ST @ base vs ST @ 18mo", 
                                                         estimate = ST_base_18mo_est, 
                                                         ci_lo = ST_base_18mo_ci_lo, 
                                                         ci_hi = ST_base_18mo_ci_hi, 
                                                         pvalue = ST_base_18mo_p,
                                                         adj_pval = exp_within_group_adj_pvals[13],
                                                         cohens_d = ST_base_18mo_est/ST_baseline_sd))

exp_within_group_contrast_results_df <- rbind(exp_within_group_contrast_results_df,
                                              data.frame(contrast = "ST @ base vs ST @ 24mo", 
                                                         estimate = ST_base_24mo_est, 
                                                         ci_lo = ST_base_24mo_ci_lo, 
                                                         ci_hi = ST_base_24mo_ci_hi, 
                                                         pvalue = ST_base_24mo_p,
                                                         adj_pval = exp_within_group_adj_pvals[14],
                                                         cohens_d = ST_base_24mo_est/ST_baseline_sd))

(exp_within_group_contrast_results_df)

#Save output table
exp_within_group_contrast_results_df <- exp_within_group_contrast_results_df %>% mutate(across(where(is.numeric), round, digits = 3))
exp_within_group_contrast_results_table_OUT <- flextable(exp_within_group_contrast_results_df) %>%
  theme_booktabs() %>%
  autofit()
save_as_docx(exp_within_group_contrast_results_table_OUT, path = "/users/Damien/Desktop/youth_BHS-4_exploratory_within_group_contrasts_table.docx")

```


8. PLOT MODEL-ESTIMATED MEANS WITH 95% CIS ACROSS ALL TIME POINTS FOR EACH SSI CONDITION
```{r }
mm_grid <- mm_grid %>%
  mutate(
    time = factor(
      time,
      levels = c("1", "2", "3", "4", "5", "6", "7", "8"),
      labels = c("baseline", "pre", "post", "3 months", "6 months", "12 months", "18 months", "24 months")
    ),
    condition = factor(condition, levels = c("ST", "BA", "GMI"))
  )

ggplot(mm_grid, aes(x = time, y = marginal_mean, group = condition)) +
  geom_line(aes(linetype = condition), linewidth = 0.8) +
  geom_point(aes(shape = condition), size = 2.5) +
  geom_errorbar(
    aes(ymin = ci_lo,
        ymax = ci_hi,
        linetype = condition),
    width = 0.10,
    linewidth = 0.6) +
  labs(x = "Measurement Occassion",
       y = "Model-Estimated Mean",
       linetype = "Condition",
       shape = "Condition",
       title = "Model-Estimated Means over Time for Youth BHS-4 across Treatment Conditions") +
  theme_classic()
  
```














